Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-09 ms.tex
explain temperature axis limits for reddening residual plots
caption for last reddening residual figure

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid.eps, width=6.6in}
\caption{\label{fig:resid} (top left) Residuals of $E(B-V)_{2comp}$ relative to
$E(B-V)_{SSPP}$ as a function of $E(B-V)_{SFD}$. The grayscale represents the 
conditional probability within each $E(B-V)_{SFD}$ bin. The central black line 
shows the moving median. The upper and lower black lines represent the moving 
75th and 25th percentiles respectively. (bottom left) Residuals of 
$E(B-V)_{2comp}$ relative to $E(B-V)_{SSPP}$ as a function of hot dust 
temperature $T_2$. (top right) Same as top left, but illustrating the residuals
of $E(B-V)_{mbb}$, our calibration of the \cite{planckdust} $\tau_{353}$ to 
$E(B-V)_{SSPP}$. (bottom right)  Same as bottom left, but showing the 
$E(B-V)_{mbb}$ residuals as a function of the single-MBB dust temperature from 
\cite{planckdust}.}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
\epsfig{file=resid_offs.eps, width=3.3in}
\caption{\label{fig:resid_offs} $E(B-V)_{2comp}$ residuals as a function of
SFD $E(B-V)$, including a cut on ecliptic latitude, $|\beta|>20^{\circ}$, 
and zero level perturbations of $\pm$0.08 MJy/sr to i100 and 
857 GHz respectively. The grayscale represents the conditional probability 
within each bin in SFD $E(B-V)$. The central black line shows the moving 
median. The upper and lower black lines represent the moving 75th and 25th 
percentiles respectively.}
\end{center}
\end{figure}

>>>>

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid.eps, width=6.6in}
\caption{\label{fig:resid} (top left) Residuals of $E(B-V)_{2comp}$ relative to
$E(B-V)_{SSPP}$ as a function of $E(B-V)_{SFD}$. The grayscale represents the 
conditional probability within each $E(B-V)_{SFD}$ bin. The central black line 
shows the moving median. The upper and lower black lines represent the moving 
75th and 25th percentiles respectively. (bottom left) Residuals of 
$E(B-V)_{2comp}$ relative to $E(B-V)_{SSPP}$ as a function of hot dust 
temperature $T_2$. (top right) Same as top left, but illustrating the residuals
of $E(B-V)_{mbb}$, our calibration of the \cite{planckdust} $\tau_{353}$ to 
$E(B-V)_{SSPP}$. (bottom right)  Same as bottom left, but showing the 
$E(B-V)_{mbb}$ residuals as a function of the single-MBB dust temperature from 
\cite{planckdust}. The temperature axes always range from the 
0.4$^{th}$ percentile to 99.6$^{th}$ percentile temperature values.}
\end{center}
\end{figure*}

@@

\begin{figure}
\begin{center}
\epsfig{file=resid_offs.eps, width=3.3in}
\caption{\label{fig:resid_offs} Two-component reddening residuals after 
restricting to high ecliptic latitude ($|\beta|>20^{\circ}$) and perturbing the
\texttt{i100} and 857 GHz zero levels by $+$0.08 MJy/sr and $-$0.08 MJy/sr 
respectively. The bending behavior as a function of $E(B-V)_{SFD}$ has been
eliminated, and virtually no temperature dependence remains.}
\end{center}
\end{figure}
